When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2020-08-25 code/Submissionv2.Rmd
commit

#next, conduct a logit regression where the DV is values of Ques_Prof along
#several IVs

logmodel <- glm(
  Ques_Prof ~ Inst_Cred_Gallup + House_distance_dim1 + MilPSoc + Dom_P + Fig_Nme, 
  family=binomial(link="logit"), 
  data=slimdata
  )

tidy(logmodel)
glance(logmodel)

# now  make prediction data using the mean institutional credibility scores.  Vary #polarization and the three topics I am interested in.

predictiondata <- tibble(House_distance_dim1=seq(min(slimdata$House_distance_dim1), max(slimdata$House_distance_dim1), by=.01), Inst_Cred_Gallup = mean(slimdata$Inst_Cred_Gallup)) %>%
crossing(Ques_Prof = c(0,1), MilPSoc = c(0,1), Dom_P = c(0,1), Fig_Nme = c(0,1))

@@

augment(logmodel, newdata = predictiondata)

predictions <- augment(logmodel, newdata=predictiondata) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions %>% arrange(.prob, .fitted, MilPSoc, Dom_P, Fig_Nme, desc(.fitted)) %>% 
  view()

# stopping point here.  now let's try some graphs
# notice that the predictions are not in (0, 1)
ggplot(predictions) +
  aes(x = .fitted) +
  geom_histogram()

@@

# demonstration: scatter log odds (x) and predicted probability (y)
# with 95% CIs
# (CIs don't look smooth in this example because .se.fit depends on X data)
predictions %>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth() 
```
```

>>>>

#next, conduct logit regressions where the DV is values of Ques_Prof along
#two IVs, political polarization and institutional credibility.

#model 1

logmodel1 <- glm(
  Ques_Prof ~ Inst_Cred_Gallup + House_distance_dim1, 
  family=binomial(link="logit"), 
  data=slimdata
  )

tidy(logmodel1)
glance(logmodel1)

# now  make prediction data using the mean institutional credibility scores.  Vary #polarization and hold institutional credibility constant.

predictiondata <- tibble(House_distance_dim1=seq(min(slimdata$House_distance_dim1), max(slimdata$House_distance_dim1), by=.01), Inst_Cred_Gallup = mean(slimdata$Inst_Cred_Gallup)) %>%
crossing(Ques_Prof = c(0,1))

@@

augment(logmodel1, newdata = predictiondata)

predictions <- augment(logmodel1, newdata=predictiondata) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions %>% arrange(.prob, .fitted, Ques_Prof, desc(.fitted)) %>% 
  view()

# now let's try some graphs
# notice that the predictions are not in (0, 1)
ggplot(predictions) +
  aes(x = .fitted) +
  geom_histogram()

@@

# demonstration: scatter log odds (x) and predicted probability (y)
# with 95% CIs
# (CIs don't look smooth in this example because .se.fit depends on X data)
predictions %>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth()

# model2

logmodel2 <- glm(
  Ques_Prof ~ House_distance_dim1 + Inst_Cred_Gallup, 
  family=binomial(link="logit"), 
  data=slimdata
  )

tidy(logmodel2)
glance(logmodel2)

# now  make prediction data using the mean institutional credibility scores.  Vary #institutional credibilty and hold political polarization constant.

predictiondata2 <- tibble(Inst_Cred_Gallup=seq(min(slimdata$Inst_Cred_Gallup), max(slimdata$Inst_Cred_Gallup), by=1), House_distance_dim1 = mean(slimdata$House_distance_dim1)) %>%
crossing(Ques_Prof = c(0,1))

predictiondata2

augment(logmodel2, newdata = predictiondata2)

predictions2 <- augment(logmodel2, newdata=predictiondata2) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions2 %>% arrange(.prob, .fitted, Ques_Prof, desc(.fitted)) %>% 
  view()

# stopping point here.  now let's try some graphs
# notice that the predictions are not in (0, 1)
ggplot(predictions2) +
  aes(x = .fitted) +
  geom_histogram()

# demonstration: scatter log odds (x) and predicted probability (y)
# with 95% CIs
# (CIs don't look smooth in this example because .se.fit depends on X data)
predictions2 %>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth() 
```
